On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-04 docs/mvfits_paper/mvf.tex
updating docs and maths with reflect_unwrap for point reflections

An explicit sktech of this is given by Alg. (\ref{alg:A_gmvp}).

@@

    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $var$ is the variance of the respective list.

@@

Here we demonstrate \gmvr{}

>>>>

An explicit sketch of this is given by Alg. (\ref{alg:A_gmvp}).

@@

    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.

@@

Let's start by applying \gmvr{} to a fiducial scalar function,
  f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
